\documentclass[11pt]{vitae}
\usepackage[ %
	pdfencoding = auto, %
	pdftitle={Curriculum Vitae},
	pdfauthor={Edward F. Brown},
	colorlinks,
	urlcolor={Goldenrod4},
	linkcolor={SteelBlue4},
]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\rhead{\thepage}
\lhead{Curriculum Vitae---Edward Brown}
\renewcommand{\headrulewidth}{0.4pt}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}
\thispagestyle{empty}
{\LARGE\scshape Edward Brown}

\parbox[t]{186pt}{%
Department of Physics and Astronomy\\
Michigan State University\\
Biomedical Physical Sciences\\
567 Wilson Road, Room 3266\\
East Lansing, MI 48824\\
USA
}
\hfill
\parbox[t]{220pt}{%
+1 517 884-5620\\
\href{mailto:ebrown@pa.msu.edu}{\texttt{ebrown@pa.msu.edu}}\\
\href{http://www.pa.msu.edu/~ebrown}{\texttt{http://www.pa.msu.edu/\symbol{126}ebrown}}\\
\href{https://github.com/nworbde}{\texttt{https://github.com/nworbde}}\\
}

\vspace{4.0ex plus1ex minus0.5ex}

\sectionheader{Education}
\begin{chronlist}
\item[1989--1993] The Ohio State University, Columbus.  BS,
  with distinction in physics, {\em summa cum laude}, and with honors
  in the liberal arts.

\item[1993--1999] University of California, Berkeley (UCB). PhD \& MA, physics.
\end{chronlist}

\sectionheader{Appointments}
\begin{chronlist}
\item[1993--1994] Space Sciences Lab, UCB. 
\item[1995--1999] Physics and Astronomy Departments, UCB. 
\item[1999--2002] Research Associate and Enrico Fermi Fellow, Enrico
  Fermi Institute, University of Chicago (UofC).  
\item[2002--2004] Research Scientist, Astronomy and Astrophysics
  Department and ASC \emph{Center for Astrophysical Thermonuclear
    Flashes},  UofC.  
\item[2004--2010] Assistant Professor, Department of Physics and Astronomy, National Superconducting Cyclotron Laboratory, Michigan State University (MSU). Affiliated with the Joint Institute for Nuclear Astrophysics (\emph{JINA}).
\item[2010--2015] Associate Professor, Department of Physics and Astronomy, National Superconducting Cyclotron Laboratory, MSU. Affiliated with \emph{JINA, JINA-CEE}.
\item[2015--] Professor, Department of Physics and Astronomy, National Superconducting Cyclotron Laboratory, MSU. Affiliated with \emph{JINA-CEE}.
\end{chronlist}

\sectionheader{Awards}
\begin{chronlist}
\item[year] You can use the \verb+chronlist+ environment for awards, committees, etc.
\end{chronlist}
\clearpage

\publicationheader{Refereed publications}
\begin{publist}

\item \href{https://ui.adsabs.harvard.edu/#abs/2017PhRvC..95b5806C/abstract}{``Lower Limit on the Heat Capacity of the Neutron Star Core''}, Cumming, A., Brown, E. F., Fattoyev, F. J., Horowitz, C. J., Page, D., and Reddy, S. 2017, {\itshape Physical Review C}, 95, 025806 (4 citations)

\item \href{https://ui.adsabs.harvard.edu/#abs/2016ApJ...833..186M/abstract}{``The Thermal State of KS 1731-260 after 14.5 years in Quiescence''}, Merritt, R. L., Cackett, E. M., Brown, E. F., et al.\ 2016, {\itshape The Astrophysical Journal}, 833, 186 (4 citations)

\item \href{https://ui.adsabs.harvard.edu/#abs/2016ApJ...831...13D/abstract}{``Urca Cooling Pairs in the Neutron Star Ocean and Their Effect on Superbursts''}, Deibel, A., Meisel, Z., Schatz, H., Brown, E. F., Cumming, A. 2016, {\itshape The Astrophysical Journal}, 831, 13 (7 citations)

\end{publist}

You can create other \verb+publist+ for invited talks, seminars, etc.

\end{document}
